DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-07-07 MDPI/Sensor Paper/template.tex
Update

Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.

@@

Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}. The student and teacher model is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively. Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al. 
\begin{table}[ht]
	\centering
	\begin{tabular}{|p{1cm}|p{12.5cm}|}
		\hline
		Work & Approach \\ 
		\hline
		\cite{03358} & Combination of Backbone Model and Soft Attention. Backbone model includes DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34\\
		\hline
		\cite{03798} & Transfer Learning with CNN based model\\
		\hline
		\cite{10348} & Transfer Learning with CNN based model including DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34, and InceptionNetV3\\
		\hline
		\cite{09418} & Transfer Learning with CNN based model including EfficientNet and SeNet. Data augmentation process used CutOut to create random sized hole considered as an inactive portion of image.\\
		\hline
		\cite{01284} & Transfer Learning with CNN based model. Data augmentation process uses RandArgument to split picture into several pictures which is used to train. DropBlock and Multi-Weight Loss Function are used to deal with the imbalanced.\\
		\hline
		\cite{06612} & GradCam and Kernel SHAP, two model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\
		\hline
		\cite{03225} & Student and Teacher Model is the combination of two model which share the memory learned with others. \\
		\hline
		\cite{12602} & SkinLinkNet uses the image whose shape is (448,488) for training. Unet and EfficientNetB0 are used for segmentation and classification task respectively.\\
		\hline
		\cite{03426} & WonderM uses the image whose shape is (600,600) created by padding for training. Unet and DenseNet are used for segmentation and classification task respectively.\\
		\hline
		\cite{03910} & MetaData including age, gender, and capture position are used to gain higher performance of the model. The models used in this paper are CNN-based model \\
		\hline
		\cite{03798} & Traditional Machine Learning Algorithms are applied including Random Forest, XGBoost, and Support Vector Machine \\
		\hline
		\cite{10348} & Matrix Factorization are applied before the softmax activation function \\
		\hline
		\cite{05045} & Isolation Forest are applied distribution skin lesion images before fedding into the softmax activation function. \\
		\hline
		\cite{10348} & Matrix Factorization are applied before the softmax activation function. \\
		\hline
	\end{tabular}
	\caption{Related Works Summary}
	\label{table:0}
\end{table}

\subsection{Objectives}
In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Data}
\subsubsection{Image Data}
The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}. There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the dataset is shown in the table below:
\FloatBarrier
\begin{table}[ht]
	\centering
	\begin{tabular}{|c c c c c c c c c|} 
		\hline
		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
		\hline
		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
		\hline
	\end{tabular}
	\caption{Data Distribution in HAM10000}
	\label{table:1}
\end{table}
\FloatBarrier
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
	\caption{Example image of each class}
	\label{fig:datadistribution}
\end{figure}
More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training the whole data is shuffled then split into two part. $90$ percent and $10$ percent of the data is used for training and validating respectively.

In the previous paper\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images. Since, this data is imbalanced, using augmented data may cause the problem of well classify on the majority of class. In this paper, instead of augmenting data, metadata is used. The way of processing metadata is discuss in MetaData section. Images in this dataset has the type of $RGB$ and shape of (450, 600). However, Each backbone need the different input size of image as well as the range of pixel value. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet dataset, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$. 
\subsubsection{Metadata}
The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position. During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.
\subsection{Model Schema}
\subsubsection{Input Schema}
Using metadata as another input is not new. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

In this paper, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described as follow:\\
\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{"Definitions/Input Schema"}
	\caption{Input Schema}
	\label{fig:input-schema}
\end{figure}\\
Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
\subsubsection{Soft-Attention}
Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]

In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps. 
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
	\caption{Soft-Attention Module}
	\label{fig:softattention}
\end{figure}
In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
\FloatBarrier
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
	\caption{Soft-Attention Module}
	\label{fig:softattentionblock}
\end{figure}
\FloatBarrier
\subsubsection{Backbone Model Architecture}
In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  
\FloatBarrier
\begin{table}[ht]
	\centering
	\begin{tabular}{|c | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
	\caption{Size and Parameters and Depth of backbone model used in this paper}
	\label{table:2}
\end{table}
\FloatBarrier

\subsubsection{Model}
The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer. It is described in the figure below:
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/MainModel}
	\caption{Overall Model Architecture}
	\label{fig:mainmodel}
\end{figure}
\section{Results}
The accuracy of all model is presented in the figure below:
\begin{table}[h]
	\begin{tabular}{| c | c | c | c |}
		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
		0.93 & 0.91 & 0.92 & 0.88\\
	\caption{Accuracy of the model with augmented data}
	\label{table:3}
\begin{table}[h]
	\begin{tabular}{| c | c | c | c | c |}
		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
\begin{table}[h]
	\begin{tabular}{| c | c | c | c |}
		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
		0.84 & 0.78 & 0.86 & 0.86\\
	\caption{Accuracy of the model with metadata}
	\label{table:4}
According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only. While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.93$ and $0.91$ respectively, their training with metadata has both the accuracy of $0.89$. Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata. On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively. This term will be discussed later on. Since, the model trained with augmented data have high accuracy, when their f1-score and the recall score of models are analyzed, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5. As a results, augmented data model dose not classify well on all class as InceptionResNetV2 trained on augmented data have $0.29$ f1-score on class df while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way. 
\begin{table}[h]
	\begin{tabular}{|c | c | c | c | c | c | c | c | c|} 
		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
		\thead{DenseNet201 +\\ Augmented Data} & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
		\thead{Resnet50 +\\ Augmented Data} & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
		\thead{VGG16 +\\ Augmented Data} & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
		\thead{NasNetMobile +\\Metadata and WeightLoss} & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
	\caption{F1-Score of each class and the mean f1-score of each model}
	\label{table:5}

However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the imbalanced term. Since this dataset is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample. Using the metadata, though still make the model bias, it dose contributes to the improvement of  the performance of the model.

\begin{table}[h]
	\centering
	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
		\hline
		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
		\hline
		\thead{DenseNet201 +\\ Augmented Data} & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
		\hline
		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
		\hline
		\thead{Resnet50 +\\ Augmented Data} & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
		\hline 	
		\thead{VGG16 +\\ Augmented Data} & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
		\hline		
		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
		\hline
		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
		\hline
		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
		\hline
		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
		\hline
		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
		\hline
		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
		\hline
		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
		\hline
		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
		\hline
		\thead{NasNetMobile +\\Metadata and WeightLoss} & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
		\hline
	\end{tabular}
	\caption{Recall score of each class and the mean recall score of each model}
	\label{table:6}
\end{table}

This problem is also true with the recall score according to table 6. DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has expected value of recall of $0.72$, $0.71$, $0.69$, $0.69$, respectively, while the combination of InceptionResNetV2, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.

As the results, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results. On the other hand, the reason why the model become much more balanced is the weighted loss function. Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. Therefore, DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$. $0.82$, respectively, as opposed to their training in akiec without weighted loss function. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.

Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. The table 8 illustrates the deeper analyzing of the three models. It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.

@@

	\begin{tabular}{|l | c | c | c | c|} 

@@

		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\

@@

		Accuracy(avg) & 0.81 & 0.78 & 0.84 & \textbf{0.86}\\

@@

		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 

@@

		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\

@@

		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\

@@

		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 

@@

		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\

@@

		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\

@@

	\caption{Deeper analyzing of mobile model}
	\label{table:7}

@@

Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2. Therefore, at the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model. The result of this experiment is illustrated in table 9.

@@

	\begin{tabular}{|l | c |}

@@

		Model & Accuracy\\

@@

		MobileNetV3Large-Layer[:270] + Soft-Attention + Metadata & 0.71 \\
		MobileNetV3Large-Layer[:266] + Soft-Attention + Metadata  & 0.73 \\
		MobileNetV3Large-Layer[:260] + Soft-Attention + Metadata  & 0.77 \\
		MobileNetV3Large-Layer[:251] + Soft-Attention + Metadata  & 0.79 \\
		MobileNetV3Large-Layer[:246] + Soft-Attention + Metadata  & 0.84 \\
		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512) + Metadata & 0.85 \\
		MobileNetV3Large-Layer[:240] + Soft-Attention + Metadata  & \textbf{0.86}\\
		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.84 \\
		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
		MobileNetV3Large & 0.85 \\ 

@@

	\caption{Deeper analyzing of MobileNetV3Large Model}
	\label{table:8}

@@

>>>>

Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to build solutions to a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.

@@

Otherwise, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021\cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively. Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al. 

@@

	\begin{tabular}{|p{1cm}|p{12.5cm}|}

@@

		Work & Approach \\ 

@@

		\cite{03358} & Combination of Backbone Model and Soft Attention. Backbone model includes DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34\\

@@

		\cite{03798} & Transfer Learning with CNN based model\\

@@

		\cite{10348} & Transfer Learning with CNN based model including DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34, and InceptionNetV3\\

@@

		\cite{09418} & Transfer Learning with CNN based model including EfficientNet and SeNet. Data augmentation process used CutOut to create random sized hole considered as an inactive portion of image.\\

@@

		\cite{01284} & Transfer Learning with CNN based model. Data augmentation process uses RandArgument to split picture into several pictures which is used to train. DropBlock and Multi-Weight Loss Function are used to deal with the imbalanced.\\

@@

		\cite{06612} & GradCam and Kernel SHAP, two model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\

@@

		\cite{03225} & Student and Teacher Model is the combination of two model which share the memory learned with others. \\
		\cite{12602} & SkinLinkNet uses the image whose shape is (448,488) for training. Unet and EfficientNetB0 are used for segmentation and classification task respectively.\\
		\cite{03426} & WonderM uses the image whose shape is (600,600) created by padding for training. Unet and DenseNet are used for segmentation and classification task respectively.\\
		\cite{03910} & MetaData including age, gender, and capture position are used to gain higher performance of the model. The models used in this paper are CNN-based model \\
		\cite{03798} & Traditional Machine Learning Algorithms are applied including Random Forest, XGBoost, and Support Vector Machine \\
		\cite{10348} & Matrix Factorization are applied before the softmax activation function \\
		\cite{05045} & Isolation Forest are applied distribution skin lesion images before fedding into the softmax activation function. \\
		\cite{10348} & Matrix Factorization are applied before the softmax activation function. \\

@@

	\caption{Related Works Summary}
	\label{table:0}

@@

\subsection{Objectives}
In this paper, the effect of metadata on classifying skin disease will be analyzed. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
\section{Materials and Methods}
\subsection{Data}
\subsubsection{Image Data}
The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}. There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the dataset is shown in the table below:

@@

	\begin{tabular}{|c c c c c c c c c|} 

@@

		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 

@@

		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\

@@

	\caption{Data Distribution in HAM10000}
	\label{table:1}

@@

\begin{figure}[h]
	\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
	\caption{Example image of each class}
	\label{fig:dataexample}
\end{figure}
More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training the whole data is shuffled then split into two part. $90$ percent and $10$ percent of the data is used for training and validating respectively.

In the previous paper\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images. Since, this data is imbalanced, using augmented data may cause the problem of well classify on the majority of class. In this paper, instead of augmenting data, metadata is used. The way of processing metadata is discuss in MetaData section. Images in this dataset has the type of $RGB$ and shape of (450, 600). However, Each backbone need the different input size of image as well as the range of pixel value. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet dataset, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$. 
\subsubsection{Metadata}
The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position. During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.
\subsection{Model Schema}
\subsubsection{Input Schema}
Using metadata as another input is not new. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

In this paper, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described as follow:
\begin{figure}[h]
	\includegraphics[width=1\linewidth]{"Definitions/Input Schema"}
	\caption{Input Schema}
	\label{fig:input-schema}
\end{figure}
Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
\subsubsection{Soft-Attention}
Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps. 
\begin{figure}[h]
	\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
	\caption{Soft-Attention Module}
	\label{fig:softattention}
\end{figure}
In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
\begin{figure}[h]
	\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
	\caption{Soft-Attention Module}
	\label{fig:softattentionblock}
\end{figure}
\subsubsection{Backbone Model Architecture}
